Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-05-05 paper/tex/paper.tex
remove results I and relabel
updates introduction and create comparison section
final (for now!) intro fixes after feedback
add potential for coauthors
update affiliations

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}

\newcommand{\floor}[1]{\textcolor{magenta}{[Floor: #1]}}
\newcommand{\selma}[1]{\textcolor{pink}{[Selma: #1]}}
\newcommand{\tom}[1]{\textcolor{ForestGreen}{[Tom: #1]}}

@@

\author[0000-0001-6147-5761]{T. Wagg}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0002-4421-4962]{F. Broekgaarden}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}

\begin{abstract}{
    \input{sections/abstract.tex}
}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/introduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method} \label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/methods.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results (I)  - Survey of the Problem} \label{sec:resultsI}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/resultsI.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results (II) - Synthetic Galaxy} \label{sec:resultsII}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/resultsII.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/discussion.tex}

\section{Conclusion \& Summary} \label{sec:conclusion}

\input{sections/conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\allowdisplaybreaks

\appendix

\input{sections/appendix.tex}

>>>>

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
\newcommand{\tom}[1]{\textcolor{ForestGreen}{[Tom: #1]}}

@@

% affiliations
\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}

\author[0000-0001-6147-5761]{T. Wagg}
\affiliation{\cfa}
\affiliation{\mpa}

\author[0000-0002-4421-4962]{F. Broekgaarden}
\affiliation{\cfa}

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{\cfa}
\affiliation{\mpa}
\affiliation{\UoA}

\author{...TBD}

\begin{abstract}{
    % \input{sections/abstract.tex}
    \noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\
}
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
\input{sections/introduction.tex}

\section{Method} \label{sec:method}
\input{sections/methods.tex}

\section{Results} \label{sec:results}
\input{sections/results.tex}

\section{Discussion} \label{sec:discussion}
\input{sections/discussion.tex}

\section{Comparison with previous studies}\label{sec:compare_studies}
\input{sections/comparisons.tex}

\section{Conclusion \& Summary} \label{sec:conclusion}
\input{sections/conclusion.tex}

@@

\allowdisplaybreaks
\appendix
\input{sections/appendix.tex}

### 2021-05-05 paper/tex/sections/introduction.tex
update affiliations

All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}. We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}. In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper. In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.

>>>>

All data produced in this study is publicly available on Zenodo \href{https://zenodo.org/record/4699713}{\faFileCode}\footnote{\url{https://zenodo.org/record/4699713}} as is the population used in our simulations \href{https://zenodo.org/record/4574727}{\faFileCode}\footnote{\url{https://zenodo.org/record/4574727}}. We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}. In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper. In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
